Home

### 2020-03-27 analysis/index.Rmd
veb-boost reference

# Model
  [polygenic model](polygenic_model.html)

@@

## For a single gene
  * [single gene](simulation-singleG.html)

@@

>>>>

# Model
  * [Polygenic model](polygenic_model.html)

@@

## For a single gene
  * [Single gene](simulation-singleG.html)

@@

# References
  * VEB-boost: Andrew's [software](https://github.com/andrewg3311/VEB.Boost) and [workflowr website](https://andrewg3311.github.io/VEB-Boost-workflowR/VEB_Boost_Derivation.html)
